A pair of co-moving, Sun-like stars with different chemical abundances:\\ a possible signature of copious rocky accretion (needs work)

### 2017-04-15 paper/ms.tex
took a stab at the abstract

% to-do list
% ----------
% - add items here
% style notes
% -----------
% - This file generates by Makefile; don't be typing ``pdflatex'' or some bullshit.
% - Line break between sentences to make the git diffs readable.
% - Use \, as a multiply operator.
% - Reserve () for function arguments; use [] or {} for outer shit.
% - Use \sectionname not Section, \figname not Figure, \documentname not Article or Paper or paper.

@@

% define macros for math
\newcommand{\given}{\,|\,}
\newcommand{\normal}{{\mathcal{N}}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\transp}[1]{{#1}^{\!\mathsf{T}}}
\newcommand{\inv}[1]{{#1}^{-1}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\vperp}{\bs{v}^\perp}
\newcommand{\propm}{\bs{\mu}}
\newcommand{\mat}[1]{\mathbf{#1}}
\renewcommand{\vec}[1]{\bs{#1}}
\newcommand{\kms}{\ensuremath{\rm km~s^{-1}}}
\newcommand{\msun}{{\rm M}_\odot}
\newcommand{\data}{\mathrm{data}}
\newcommand{\snr}{[S/N]_\varpi}
\newcommand{\eye}{\mathbb{I}}
\newcommand{\absdvtan}{\ensuremath{|\Delta\vec v_\mathrm{t}|}}
\newcommand{\estimates}{\ensuremath{\{\hat{\varpi_i},\hat{\mu_{\alpha,i}},\hat{\mu_{\delta,i}},\hat{v_{r,i}}\}}}

@@

\title{NEED A BETTER TITLE: A co-moving pair of bright stars \\
  with very different metallicities and abundances}

@@

\begin{abstract}
  We report and discuss the discovery of a co-moving pair of bright stars,
  HD 240429 and HD 240430, with their detailed abundances measured.
  The kinematics of the two stars from Gaia proper motions and spectroscopic RVs
  are completely consistent with them co-moving in space.
  Yet, the metallicities and the abundances of XX elements between the stars
  separated by $\sim 0.6$~pc in space are very different,
  challenging the simple picture that these co-moving pairs are once wide binaries
  formed in a coeval star-forming event but now tidally stripping.
  We consider such and such scenarios of the formation of such pairs.
\end{abstract}

>>>>

% to-do list
% ----------
% - add items here

% style notes
% -----------
% - This file generates by Makefile; don't be typing ``pdflatex'' or some bullshit.
% - Line break between sentences to make the git diffs readable.
% - Use \, as a multiply operator.
% - Reserve () for function arguments; use [] or {} for outer shit.
% - Use \sectionname not Section, \figname not Figure, \documentname not Article or Paper or paper.

@@

% define macros for math
\newcommand{\given}{\,|\,}
\newcommand{\normal}{{\mathcal{N}}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\transp}[1]{{#1}^{\!\mathsf{T}}}
\newcommand{\inv}[1]{{#1}^{-1}}
\newcommand{\bs}[1]{\boldsymbol{#1}}
\newcommand{\vperp}{\bs{v}^\perp}
\newcommand{\propm}{\bs{\mu}}
\newcommand{\mat}[1]{\mathbf{#1}}
\renewcommand{\vec}[1]{\bs{#1}}
\newcommand{\kms}{\ensuremath{\rm km~s^{-1}}}
\newcommand{\msun}{{\rm M}_\odot}
\newcommand{\pc}{{\rm pc}}
\newcommand{\data}{\mathrm{data}}
\newcommand{\snr}{[S/N]_\varpi}
\newcommand{\eye}{\mathbb{I}}
\newcommand{\absdvtan}{\ensuremath{|\Delta\vec v_\mathrm{t}|}}
\newcommand{\estimates}{\ensuremath{\{\hat{\varpi_i},\hat{\mu_{\alpha,i}},\hat{\mu_{\delta,i}},\hat{v_{r,i}}\}}}

@@

\title{A pair of co-moving, Sun-like stars with different chemical abundances:\\
       a possible signature of copious rocky accretion (needs work)}

@@

\begin{abstract}
  We report and discuss the discovery of a co-moving pair of bright solar-type
  stars, HD 240429 and HD 240430, with significant differences in their chemical
  abundance patterns.
  The two stars are co-spatial $|\Delta \bs{x}| < XX~\pc$ at a distance of
  $r\approx 100~\pc$ with nearly identical three-dimensional velocity vectors
  ($|\Delta \bs{v}| < XX~\kms$ with 95\% confidence), as inferred from \gaia\
  \tgas\ proper motions and high signal-to-noise radial-velocity measurements.
  Both stars are young with ages $\approx$$500~{\rm Myr}$ as estimated from
  their lithium abundances, favoring the idea that these were born together and
  are or were recently a bound, wide binary system.
  However, the metallicities and chemical abundances of high
  condensation-temperature elements of the two stars are very different,
  challenging this simple picture.
  We consider formation scenarios in which the pair either (1) formed together
  with identical abundances but later accreted very different quantities of
  protoplantary, rocky material, (2) were born together but with very different
  metal abundances, or (3) interacted with a field star or binary and exchanged
  a member.
  We favor scenario (1), in which the star HD 240430 consumed $\approx$10's of
  Earth masses of rocky material in small units (many rocky bodies rather than
  a few giant planets).
  Direct-imaging and precision radial-velocity follow-up to study the existence
  or properties of planetary systems around these stars would help distinguish
  these scenarios.
\end{abstract}
